\thetitle

### 2008-01-21 models.tex
Fixed up formatting of TOM classes.

\multicolumn{1}{c}{\textbf{Level}} &
\multicolumn{1}{c}{\textbf{Sub-model}} &

@@

& \multirow{1}{*}[-0.05em]{\submodel{Trace}} &

@@

& \multirow{1}{*}[-0.05em]{\submodel{Nonparametric}} &

@@

& \multirow{1}{*}[-0.05em]{\submodel{Parametric}} &

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} nodes assigned as flow end-points by sampling from fitted BiPareto model\raisebox{1.5pt}{\scriptsize*}

@@

& \multirow{1}{*}[-0.05em]{\submodel{Uniform}} &

@@

\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow sampled from fitted Lognormal model\raisebox{1.5pt}{\scriptsize*} \\
\raisebox{1.5pt}{$\centerdot$} flow size sampled from fitted BiPareto model\raisebox{1.5pt}{\scriptsize*} \\

@@

\raisebox{1.5pt}{$\centerdot$} packet sizes and intervals drawn from fitted Exponential distributions\raisebox{1.5pt}{\scriptsize*}

>>>>

\multicolumn{1}{c}{\textbf{Class}} &
\multicolumn{1}{c}{\textbf{Subclass}} &

@@

& \multirow{1}{*}[-0.05em]{\class{Trace}} &

@@

& \multirow{1}{*}[-0.05em]{\class{Nonparametric}} &

@@

& \multirow{1}{*}[-0.05em]{\class{Parametric}} &

@@

\raisebox{1.5pt}{$\centerdot$} session start time assigned according to Poisson arrival model \\
\raisebox{1.5pt}{$\centerdot$} nodes assigned as flow end-points by sampling from fitted BiPareto model

@@

& \multirow{1}{*}[-0.05em]{\class{Uniform}} &

@@

\raisebox{1.5pt}{$\centerdot$} start time relative to previous flow sampled from fitted Lognormal model \\
\raisebox{1.5pt}{$\centerdot$} flow size sampled from fitted BiPareto model \\

@@

\raisebox{1.5pt}{$\centerdot$} packet sizes and intervals drawn from fitted Exponential distributions

### 2008-01-21 paper.tex
Fixed up formatting of TOM classes.

\newcommand{\thetitle}{On the Inadequacy of Uniform Modeling for WLAN Workload Generation}

@@

\newcommand{\Section}[1]{\hyperref[sec:#1]{Section~\ref*{sec:#1}}}
\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsf{\footnotesize{#1}}}
\newcommand{\submodel}[1]{\textsf{\footnotesize{#1}}}
\newcommand{\model}[1]{#1}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

We define a range of sub-models at each level of the \caps{TOM}, with decreasing similarity to the original trace behavior: \submodel{Trace} (reproduce original behavior), \submodel{Nonparametric}, \submodel{Parametric}, and \submodel{Uniform}. The control model uses the Trace sub-model at every level, exactly reproducing the behavior recorded from the original network. The standard na\"ive model uses the \submodel{Uniform} sub-model at all levels. The models proposed by {\FHC} are implemented using the \submodel{Parametric} sub-model at every level. The \submodel{Nonparametric} sub-models provide a measure of how much error is introduced by parametric approximation and parameter estimation.

@@

This work extends that published in~\cite{Karpinski07:realism}~and~\cite{Karpinski07:cbr-failure}, using the same methodology for defining and quantifying the realism of synthetic traffic models. The Traffic Object Model builds on the combinatorial approach taken in~\cite{Karpinski07:cbr-failure}, while providing an flexible and general object-oriented framework for constructing generative traffic models. The traffic models evaluated here overlap and augment those evaluated in both prior works; comparison with the models proposed in {\FHC} is entirely new. The Qualnet simulation methodology has been enhanced by the implementation of full-duplex, trace-driven raw \caps{IP}, \caps{TCP}, and \caps{UDP} flows, and performance metric collection based on the \caps{IETF} recommendations for \caps{IP} performance metrics framework~\cite{rfc:ip-metrics,rfc:jitter}.

@@

\begin{table}[t]
\vspace{0.75em}
\begin{center}
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{2.7in}
\begin{small}
\vspace{0.6em}
\input{properties.tex}
%\vspace{0.6em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\end{center}
\vspace{-0.5em}
\caption{Classes and their attributes in the Traffic Object Model.}
\vspace{-2em}
\end{table}

@@

\begin{table*}[t]
\begin{center}
\small
\input{models.tex}
\footnotesize\\[0.5em]
\raisebox{1pt}{*}Parametric models fitted to inherited empirical distributions using maximum likelihood estimation ({\scriptsize{MLE}}).
\end{center}
\vspace{-0.75em}
\label{fig:properties}
\caption{Summary of how the sub-models at each behavioral level of the {\footnotesize{TOM}} delegate, override or inherit properties.}
\vspace{-1.75em}
\end{table*}

In this section, we present a generic object-oriented framework for implementing traffic generation models. This framework is called the Traffic Object Model (\caps{TOM}). It defines four levels of responsibility: network, node, flow and packet. The framework is designed so that different behaviors at each level can be naturally implemented  as classes in object-oriented programming languages. The framework automatically gains the advantages of object orientation, in particular modularity and encapsulation. Every traffic model is naturally split into separate spheres of responsibility, which constitute sub-models for the aspects of the model's behavior at each layer. Thanks to encapsulation and polymorphism of objects, the sub-models from different models can immediately be recombined to create new hybrid behaviors. It is trivial, for example, to produce trace-based node behavior, coupled with parametric flow behavior, and uniform packet behavior. Not all combinations of sub-models are valid, however; which classes may be combined depends on the details of each class. The ability to mix-and-match aspects of behavior at different levels greatly enhances our ability to explore the space of possible traffic models.

%For example, to use uniform flow behavior but non-uniform, trace-based node behavior, simply mix the the uniform implementation of the

Abstract base classes define the properties at each level that traffic models must implement.\footnote{In Java or C\#, this role may be played either by an actual abstract class or by an interface. In duck-typed languages such as Ruby or Python, no actual abstract class need exist, since type is implicitly defined by usage; if inheritance is desired, the base class can be made abstract by defining stub methods that throw informative exceptions if called.} Figure~\ref{fig:properties} enumerates all the properties exposed by traffic models used in this work. Other traffic models may necessitate exposing additional properties, but this list suffices to implement the models used in this paper. Concrete classes implement the behavior of specific traffic models at each level. A complete synthetic workload is created as follows:
\begin{enumerate}
\item instantiate a \class{Network} object of the appropriate class;
\item the top-level \class{Network} object in turn instantiates a collection of \class{Node} objects and associated \class{Flow} objects;
\item each \class{Flow} object generates a stream of \class{Packet} objects.
\end{enumerate}
The hierarchy of objects may be used to directly drive a simulation, or may generate configuration files that in turn drive a simulation. Our implementation does the latter, generating a collection of Qualnet configuration files and trace files specific to each workload instantiation (see \Section{simulations}).

@@

>>>>

\newcommand{\thetitle}{On the Inadequacy of Uniform Modeling for Wireless LAN Workload Generation}

@@

\newcommand{\Section}[1]{\hyperref[sec:#1]{Section~\ref*{sec:#1}}}
\newcommand{\FHC}{Hern\'andez-Campos~\textit{et~al.}}
\newcommand{\class}[1]{\textsc{\small{#1}}}
\newcommand{\model}[1]{#1}
\newcommand{\RFC}[1]{\caps{RFC}~{#1}}

@@

We define a range of sub-models at each level of the \caps{TOM}, with decreasing similarity to the original trace behavior: \class{Trace} (reproduce original behavior), \class{Nonparametric}, \class{Parametric}, and \class{Uniform}. The control model uses the Trace sub-model at every level, exactly reproducing the behavior recorded from the original network. The standard na\"ive model uses the \class{Uniform} sub-model at all levels. The models proposed by {\FHC} are implemented using the \class{Parametric} sub-model at every level. The \class{Nonparametric} sub-models provide a measure of how much error is introduced by parametric approximation and parameter estimation.

@@

This work extends that published in~\cite{Karpinski07:realism}~and~\cite{Karpinski07:cbr-failure}, using the same methodology for defining and quantifying the realism of synthetic traffic models. The Traffic Object Model builds on the combinatorial approach taken in~\cite{Karpinski07:cbr-failure}, while providing an flexible and general object-oriented framework for constructing generative traffic models. The traffic models evaluated here overlap and augment those evaluated in both prior works; comparison with the models proposed in {\FHC} is entirely new. The Qualnet simulation methodology has been enhanced by the implementation of full-duplex, client-server, trace-driven raw \caps{IP}, \caps{TCP}, and \caps{UDP} flows. We have also implemented performance metric aggregation based on the \caps{IETF} framework for \caps{IP} performance metrics~\cite{rfc:ip-metrics,rfc:jitter}.

@@

\begin{table}[t]
\vspace{0.75em}
\begin{center}
\begin{tabular}[t]{|l|}
\hline
\begin{minipage}[l]{2.7in}
\begin{small}
\vspace{0.7em}
\input{properties.tex}
%\vspace{0.6em}
\end{small}
\end{minipage}
\\\hline
\end{tabular}
\end{center}
\vspace{-0.5em}
\caption{{\footnotesize{TOM}} base classes and their attributes.}
\label{tab:properties}
\vspace{-2em}
\end{table}

@@

\begin{table*}[t]
\begin{center}
\small
\input{models.tex}
\footnotesize\\[0.5em]
%\raisebox{1pt}{*}Parametric models fitted to inherited empirical distributions using maximum likelihood estimation ({\scriptsize{MLE}}).
\end{center}
\vspace{-0.75em}
\caption{Details of how the sub-models at each behavioral level of the {\footnotesize{TOM}} inherit, override and delegate properties.}
\label{tab:models}
\vspace{-1.75em}
\end{table*}

In this section, we present a generic object-oriented framework for implementing traffic generation models. This framework is called the Traffic Object Model (\caps{TOM}). It defines four levels of responsibility: network, node, flow and packet. The framework is designed so that different behaviors at each level can be naturally implemented  as classes in object-oriented programming languages. The framework automatically gains the advantages of object orientation, in particular modularity and encapsulation. Every traffic model is naturally split into separate spheres of responsibility, which constitute sub-models for the aspects of the model's behavior at each layer. Encapsulation and polymorphism of objects, allows us to mix-and-match the sub-models from different models to create new hybrid behaviors. It is trivial, for example, to produce trace-based node behavior, coupled with parametric flow behavior, and uniform packet behavior. Not all combinations of sub-models are valid, however; which classes may be combined depends on the details of each class.

Abstract base classes define the properties at each level that traffic models must implement.\footnote{In Java or C\#, this role may be played either by an actual abstract class or by an interface. In duck-typed languages such as Ruby or Python, no actual abstract class need exist, since type is implicitly defined by usage; if inheritance is desired, the base class can be made abstract by defining stub methods that throw informative exceptions if called.} 
Table~\ref{tab:properties} enumerates all the properties exposed by traffic models used in this work. Other traffic models may necessitate exposing additional properties, but this list suffices to implement the models used in this paper. Concrete classes implement the behavior of specific traffic models at each level. A complete synthetic workload is instantiated as follows:
\begin{enumerate}
\item create a \class{Network} object of the appropriate class;
\item the top-level \class{Network} object in turn instantiates a collection of \class{Node} objects and associated \class{Flow} objects;
\item each \class{Flow} object generates a stream of \class{Packet} objects.
\end{enumerate}
The hierarchy of objects may be used to directly drive a simulation, or may generate configuration files that in turn drive a simulation. Our implementation does the latter, generating a collection of Qualnet configuration files and trace files specific to each workload instantiation (see \Section{simulations}).

@@

For each of the \class{Node}, \class{Flow} and \class{Packet} abstract classes, we create define four concrete subclasses: \class{Trace}, \class{Nonparametric}, \class{Parametric} and \class{Uniform}. The \class{Trace} class at each level takes its properties directly from the behavior of the original traffic. The \class{Nonparametric} and \class{Parametric} classes use nonparametric models of marginal behavior at each level to
